\section{Academic Committee}

\subsection{Ratified}
August 22, 2019

\subsection{Mandate}
A Standing Committee (Bylaws 2.9.5.1) of the Society, the mandate of the Academic Committee is to highlight graduate student members at the University of Western Ontario in an academic and research context. This policy is a mandatory list of initiatives that the Academic Committee must undertake in any given year. Here, the aim is to ensure a successful organization of student presenters and guest speakers at the Western Research Forum (WRF).

\subsection{Article I: Membership}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item The Academic Committee shall have:
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item An Official Liaison, who shall be the Vice-President Academic and shall be a voting ex-officio member, in compliance with Bylaws 2.9.3.2 and 2.9.3.3.
	\end{longenum}
\item The Academic Committee will elect:
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item One Chairperson or two Co-Chairs, who shall:
		\begin{longenum}[ label*=\arabic*., align=left] 
		\item Be elected from amongst the committee members;
		\item Act in compliance with the Duties of the Chairperson (Bylaw 2.9.2.);
		\item And fulfill the duties in Bylaw 2.9.5.11.1;
		\end{longenum}
	\end{longenum}
\item The Academic Committee shall have:
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item A membership limit, as per Bylaw 2.9.4.2.2., set at 16 voting members, including the Chair(s).
	\item Ideally a minimum of one (1) member of the Society from the following four (4) divisions: Arts, Biosciences, Physical Sciences, and Social Sciences.
	\end{longenum}
\item All voting members of the Academic Committee shall be:
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item Full and associate members of the Society nominated to the committee by the Society's Council.
	\end{longenum}
\end{longenum}		

\subsection{Article II: Committee Management}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item The Academic Committee will act in accordance with Bylaw 2.9.3.5 and 2.9.3.7 to determine quorum, Bylaw 2.9.3.9 to manage and maintain attendance, and Bylaw 2.9.4.2.1 to count votes.
\item Voting Policies
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item Aside from the scheduled meetings, online voting is also permitted on the condition that it is for correcting spelling, grammar, or wording mistakes on motions. Voting members shall be given one (1) business day to respond to an online vote, at which point the vote shall be considered concluded. If any voting member objects to business being voted on online, the voting shall be prohibited for that particular piece of business.
	\item Committee members (including the Official Liaison, Chair(s), and ex-officio members) can hold up to three (3) proxies.
	\end{longenum}
\item Non-committee members may attend as non-voting guests if invited by the chair. Committee members may also request that non-committee members attend as non-voting guests.
\item As per Bylaw 1.6.5. the Chair(s) and voting members may serve no more than 12 consecutive months without being ratified for a new council year.
\item Respectful Abandonment: In the event of the failure of a voting member of the committee to attend two meetings during their term either in person or by proxy, the Chair(s) may remove the member from the committee in accordance with the protocols listed in Bylaw 2.9.3.9.
\item Positions within the Academic Committee shall include:
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item Promotions, Advertisement and Social Media Manager(s), who will be responsible for on-campus promotion and actively maintaining a social media presence for the purpose of promoting the WRF; 
	\item A Recording Secretary, who will be responsible for keeping committee meeting minutes;
	\item Abstract Review Officer(s), who will be responsible for overseeing the abstract review process;
	\item Communication Officer(s), who will be responsible for maintaining contact with potential WRF presenters/speakers and point person(s).
	\end{longenum}
\end{longenum}		

\subsection{Article III: Operations}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item The Academic Committee shall:
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item Organize and run the WRF, which highlights and showcases graduate student member research from all disciplines. Responsibilities include:
		\begin{longenum}[ label*=\arabic*., align=left] 
		\item Developing short- and long-term goals for the WRF;
		\item Promoting the WRF through all available channels;
		\item Ensuring the quality of the WRF;
		\item Providing instructions for presenters and guest speakers;
		\item Aiming to appeal to various audiences at the WRF, including undergraduate students, other graduate students, the Western University campus, and the general community.
		\end{longenum}
	\item Aim to keep the following timeline:
		\begin{longenum}[ label*=\arabic*., align=left] 
		\item September: Call-out for committee members 
		\item December: Abstract submission deadline
		\item January: Abstract review deadline
		\item February: Finalize itinerary for WRF (e.g., confirm speakers and presenters)
		\item March: WRF
		\item April: WRF debrief (the Academic Committee) and Scholarship@Western platform updated.
		\end{longenum}
	\item maintain WRF’s online platform through Scholarship@Western.
		\begin{longenum}[ label*=\arabic*., align=left] 
		\item In an effort to promote environmentally friendly operations, an online (web-based) format only will be used.
		\item Abstracts will be submitted and reviewed through the Scholarship@Western platform.
		\item The conference program will be uploaded to the Scholarship@Western website one (1) month before the event.
		\item Conference proceedings, abstracts, photos, and any supplementary material will be uploaded to the Scholarship@Western website within two (2) weeks following the event.
		\end{longenum}
	\item Adjudicate the 125th Anniversary Scholarship:
		\begin{longenum}[ label*=\arabic*., align=left] 
		\item This policy is a recommended procedure for the distribution of the 125th Anniversary Scholarship, an award valued at \$1,250 which is currently awarded once a year to four (4) members of the Society of Graduate Students on the basis of academic achievement, research excellence, and community involvement who are receiving less in internal or external funding than the amount of tuition.
		\item Prior to receipt of the award, the SOGS accountant should confirm with the School of Postgraduate and Doctoral Studies that the application does accurately reflect the financial situation of the member.
		\item As a result of the stipulation that applicants be receiving less in internal or external funding than the amount of tuition paid, the scholarship often receives fewer applicants who meet the requirements than awards are available. The Academic Committee of 2011-2012 therefore recommends that the succeeding Academic Committee review the criteria and make appropriate changes to allow for a greater number of potential candidates. Recommendations are outlined in the “Recommendations for Succeeding Vice Presidents Academic of the Society of Graduate Students”. This policy document should thereafter be modified to reflect the criteria for success.
		\end{longenum}
	\item Be responsible for adjudicating other awards that the Society may wish to administer.
	\item Advertise other organized and supported activities as per the Society.
	\end{longenum}
\item The Society encourages the presence of all executives and non-executives at the WRF.
\end{longenum}	