\section{Bylaws and Constitution Committee}

\subsection{Ratified}
September 20, 2021

\subsection{Mandate}
As per Bylaw 2.9.4.1, the Bylaws and Constitution Committee (BCC) is a standing committee of the Society of Graduate Students. As per the Society's Bylaws 2.9.5.3, the committee is responsible for devising new and reviewing standing bylaws to reflect the current needs and wishes of the Society, and to allow the specific elaboration, interpretation, and application of the Society's Constitution. The Bylaws and Constitution Committee works in conjunction with the Policy Committee to ensure consistency and cohesion within the Society's unified governing documents.

\subsection{Article I: Membership}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item The Bylaws and Constitution Committee shall include:
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item An official liaison, who shall be the Speaker, and who shall be a non-voting member of the committee in compliance with Bylaws 2.9.3.2 and 2.9.3.3.
	\item A Chairperson, who shall be chosen from amongst the committee members, and whose duties and responsibilities are outlined in Bylaws 2.9.2. and 2.9.5.3.5. The Chairperson of the BCC shall also:
		\begin{longenum}[ label*=\arabic*., align=left] 
		\item serve as Deputy Speaker (see Bylaws \ref{DS:bylaws})
		\item serve, ex-officio, as Deputy Chief Returning Officer (see Bylaws 2.2.4)
		\item be a voting, ex-officio member of the Policy Committee.
		\end{longenum}
	\item A Deputy Chairperson, in compliance with Bylaw 2.9.5.3.6.
	\item The Chairperson of the Policy Committee, who shall be a voting ex–officio member.
	\end{longenum}
\item Other voting members of the BCC shall be members of the Society nominated to the committee by the Society's Council.
\item Membership, including the Chairperson and Deputy Chairperson, but excluding the ex-officio members, shall be capped at 20 (as per the request of the Society Council).
\end{longenum}

\subsection{Article II: Committee Management}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item Committee Meetings
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item The BCC shall endeavour to meet on a monthly basis in order to ensure that the governing documents of the Society are regularly reviewed.
	\item The BCC shall endeavour to schedule meetings in the week prior to the deadline for submissions to the Society's Council Package, in order to ensure that any motions pertaining to the governing documents of the Society are afforded the opportunity for review.
	\item Respectful Abandonment: In the event of the failure of a voting member of the committee to attend two meetings during their term either in person or by proxy, the Chair may remove the member from the committee in accordance with the protocols listed in Bylaw 2.9.3.9.
	\item Non-committee members may attend as non-voting guests if invited by the Chair. Committee members may also request that non-committee members attend as non-voting guests.
	\end{longenum}

\item Voting Policies
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item The BCC  will act in accordance with Bylaw 2.9.3.5 and 2.9.3.7 to determine quorum, and with Bylaw 2.9.4.2.1 to count votes.
	\item Committee members, including Ex-officio, can hold up to three (3) proxies.
	\item Outside of scheduled meetings, online voting is permitted with the following procedures:

		\begin{longenum}[ label*=\arabic*., align=left] 	
		\item Voters are given at least one (1) full business day to respond to an online vote relating to amendments to spelling, grammar, or wording errors, at which point the vote shall be considered concluded;
		\item Voters are given at least three (3) full business days to respond to an online vote relating to any other business items that were on the agenda and discussed at the previous committee meeting, at which point the vote shall be considered concluded;
		\item If any voting member objects to business being voted on online, the voting shall be prohibited for that particular piece of business.	
		\end{longenum}	
\item Roles and responsibilities:
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item The Chairperson shall:
		\begin{longenum}[ label*=\arabic*., align=left] 
		\item Serve a one-year term commencing July 1st;
		\item Shall follow the duties and responsibilities of their position outlined in Bylaws 2.2.4. The Deputy Chief Returning Officer (DCRO) and \ref{DS:bylaws} Deputy Speaker;
		\item Call, at minimum, monthly meetings of the Committee;
			\begin{longenum}[ label*=\arabic*., align=left] 
			\item Proposed meeting dates should be sent out at least two weeks in advance of the monthly meeting of the committee;
			\item Members should be given at least one week's notice prior to the meeting date.
			\end{longenum}
		\item Ensure minutes are taken in accordance with Policy 3.4. Minutes Writing Policy;
		\item Submit a written report at least once per year at the Society's Annual General Meeting, per 2.9.2.11.;
		\item Submit business for consideration at Council on behalf of the Bylaws and Constitution Committee in accordance with the procedure outlines in Bylaw 2.15.3.7.;
		\item Submit committee minutes to the Speaker by the most imminent Package Deadline following the committee meeting for ratification at Council; 
		\item Submit each committee member's name for re-ratification at the June Council meeting;
		\item Update the BCC Chair Transitional Manual at the end of their term, and submit it for review to the Speaker, before stepping down and/or graduating.	
		\end{longenum}
	\item Voting members of the committee shall:
		\begin{longenum}[ label*=\arabic*., align=left] 
		\item Endeavour to regularly attend committee meetings;
		\item Endeavour to adequately prepare for and participate at committee meetings;
		\item Assign their proxy to another member of the committee, should they be unable to attend a meeting for any reason;
		\item Vote to approve minutes and motions, and in elections (i.e., of the Deputy Speaker and BCC Deputy Chairperson);
		\item Adhere to Bylaws 2.1.1. and Policy 3.1. in the Unified Documents, related to Conflict of Interest.
		\end{longenum}
	\item The Official Liaison (the Speaker) shall:
		\begin{longenum}[ label*=\arabic*., align=left] 
		\item Be primarily concerned to foster, organize, and mobilize the participation of the membership by dedicating themselves to ensuring that the Committee:
			\begin{longenum}[ label*=\arabic*., align=left] 
			\item Has members;		 
			\item Meets on a regular basis.		
			\end{longenum}
		\item Offer neutral insight into the reading of the Society's governing documents and proposed amendments.
		\end{longenum}
	\end{longenum}
\end{longenum}
\end{longenum}


\subsection{Article III: General Operations}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item The BCC shall:
	\begin{longenum}[ label*=\arabic*., align=left] 
	\item Support the Society in drafting motions;
	\item Devise new and recommend amendments to standing Constitution articles and Bylaws to reflect the current needs and wishes of the Society;
	\item Make recommendations and/or motions to Council on governance-based topics on Council's mandate.
	\end{longenum}
\end{longenum}



\subsection{Article IV: Governing Documents}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item The BCC shall conduct a yearly review of the Society's Constitution and Bylaws to ensure consistency and cohesion within the Society's unified governing documents.
\item Constitution of the Society: Amendments to the Society's Constitution will follow the directives outlined in section 1.8.1 (Amendments to the Constitution).
\item Bylaws of the Society: Amendments to the Bylaws shall be dealt with in the same manner as amendments to the Constitution, except that they need not be approved by a General Meeting before coming into effect.
\item Operations and Policies of the Society: The BCC shall support the Policy Committee to maintain the Policy documents of the Society, as well as in drafting motion-based policies.
\end{longenum}

\subsection{Article IV: Dissemination of Amendments}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item In accordance with the Constitution of the Society (1.8.3), amendments to the Constitution that have been ratified at a General Meeting or updates to the Bylaws or Policy Documents that have been ratified at Council shall be both published in the complete form of their respective document and announced to the membership within two (2) months of ratification.
\end{longenum}


















