\section{GradCast Editorial Board}

\subsection{Ratified}
August 22, 2019

\subsection{Mandate}
A standing committee (Bylaws 2.9.5.9) of the Society, the mandate of the GradCast Editorial Board committee is to highlight graduate students at the University of Western Ontario in a media context.

\subsection{Article 1: Membership} 
\begin{enumerate} [label*=\arabic*., align=left]	
\item The Gradcast Editorial Board shall have: 
\begin{enumerate}[label*=\arabic*., align=left]	
\item An Official Liaison, who shall be the Vice-President Academic. 
\end{enumerate}
\item The GradCast Editorial Board Committee will elect:
\begin{enumerate}[label*=\arabic*., align=left]
\item A Chairperson, who shall:
\begin{enumerate}[label*=\arabic*., align=left]
\item be elected (also known as the Managing Editor) from amongst the committee members; 
\item act in compliance with the Duties of the Chairperson (Bylaw 2.9.2);
\item and fulfill the duties in Bylaw 2.9.5.11.1;
\item A Deputy Chairperson (if applicable), who shall assume the duties of the Chairperson at the discretion of the Chairperson or the committee or in the absence of the Chairperson.
\end{enumerate}
\item  The GradCast Editorial Committee will have:
\begin{enumerate}[label*=\arabic*., align=left]
\item A membership limit, as per Bylaw 2.9.4.2.2., set at 15 voting members, including the Chairperson and Deputy Chairperson (if applicable).
\end{enumerate}
\item The GradCast Editorial Committee will aim to include at least one member from each of the following divisions: Arts, Biosciences, Physical Sciences, and Social Sciences.
\item All voting members of the GradCast Editorial Committee shall be full and associate members of the Society nominated to the committee by the Society’s Council.
\end{enumerate}
\end{enumerate}

\subsection{Article II: Committee Management}
\begin{enumerate}[label*=\arabic*., align=left]
\item The GradCast Editorial Committee will act in accordance with Bylaw 2.9.3.5 and 2.9.3.7 to determine quorum, Bylaw 2.9.3.9 to manage and maintain attendance, and Bylaw 2.9.4.2.1 to count votes.
\item Voting Policies
\begin{enumerate}[label*=\arabic*., align=left]	
\item Aside from the scheduled meetings, online voting is also permitted on the condition that it is for correcting spelling, grammar, or wording mistakes on motions. Voting members shall be given one (1) business day to respond to an online vote, at which point the vote shall be considered concluded. If any voting member objects to business being voted on online, the voting shall be prohibited for that particular piece of business.
\item Committee members (including the Official Liaison, Chairperson, Deputy Chairperson, and ex-officio members) can hold up to three (3) proxies.
\end{enumerate}
\item Positions within the GradCast Editorial Board shall include:
\begin{enumerate}[label*=\arabic*., align=left]
\item A Promotions, Advertisement and Social Media Manager, who will be responsible for actively maintaining a social media presence for GradCast;
\item A Recruitment Officer, who will be responsible for actively recruiting students to the show;
\item A Recording Secretary, who will be responsible for keeping and disseminating committee meeting minutes.
\end{enumerate}
\item Non-committee members may attend as non-voting guests if invited by the chair. Committee members may also request that non-committee members attend as non-voting guests.
\item Bylaw 1.6.5. the Chairperson, and voting members may serve no more than 12 consecutive months without being ratified for a new council year.
\item Respectful Abandonment: In the event of the failure of a voting member of the committee to attend two meetings during their term either in person or by proxy, the Chair(s) may remove the member from the committee in accordance with the protocols listed in Bylaw 2.9.3.9.
\end{enumerate}

\subsection{Article III: Operations}
\begin{enumerate} [label*=\arabic*., align=left]	
\item The GradCast Editorial Board shall:
\begin{enumerate}[label*=\arabic*., align=left]	
\item Advertise for submissions in compliance with Bylaw 2.9.5.9.3;
\item Provide instructions for contributors – episode producer(s), guest(s), and host(s) – in compliance with Bylaw 2.9.5.9;
\item Maintain a schedule of guests on a shared online document;
\item Once a term, or as needed, host a recruitment event;
\item Endeavor to promote GradCast episodes through all available channels;
\item Ensure the quality of each GradCast episode;
\item Display the official logo for GradCast on all websites and social media platforms;
\item Designate at least one (1) member to complete all mandatory CHRW training;
\item Designate a producer for each episode, who shall:
\begin{enumerate}[label*=\arabic*., align=left]
\item Be present at the recording session and set up recording equipment;
\item Instruct the host(s) and guest(s) on proper recording etiquette;
\item Within one week from recording, edit the podcast and include the GradCast jingle to the beginning and end of the episode;
\item Upload each episode to Podbean with title, summary, and photo;
\item Upload each episode to CHRW’s shared folder for the station to air.
\end{enumerate}
\end{enumerate}
\item The GradCast radio show and podcast shall aim to:
\begin{enumerate}[label*=\arabic*., align=left]	
\item highlight and showcase student research;
\item appeal to various audiences including other graduate students, the Western University campus, and the general community;
\item maintain episodes at approximately 30 minutes in length on a weekly basis or as designated by CHRW;
\item maintain at least one (1) pre-recorded podcast episode to maintain a weekly schedule as needed should circumstances arise;
\item be comprised of at least one (1) student guest per episode.
\end{enumerate}
\item The GradCast website shall:
\begin{enumerate}[label*=\arabic*., align=left]	
\item be updated on a regular basis to keep up to date with guest appearances;
\item bear the official GradCast logo;
\item aim to include a picture of guests and hosts, along with a brief caption summarizing the topic of the episode.
\end{enumerate}
\end{enumerate}