\section{Health Plan Committee}

\subsection{Ratified}
August 22, 2019

\subsection{Mandate}
As per Bylaw 2.9.4.1., the Health Plan Committee (HPC) is a standing committee of the Society of Graduate Students (SOGS). As per the Society’s Bylaws (2.9.5.13), the HPC shall: review and recommend changes to the Society’s health plan and health plan policies, review health plan bids and contracts, provide shortlists to Council, and work in consultation with the Vice-President Student Services to help run and promote mental health and wellness initiatives (e.g. Graduate Wellness Week) for members of the society.

\subsection{Article I: Membership}
\begin{enumerate}[label*=\arabic*., align=left]	
\item The Health Plan Committee (HPC) shall have:
\begin{enumerate}[label*=\arabic*., align=left]	
\item An Official Liaison, who shall be the Vice-President Student Services. 
\end{enumerate}
\item The Health Plan Committee will elect:
\begin{enumerate}[label*=\arabic*., align=left]
\item A Chairperson, who shall:
\begin{enumerate}[label*=\arabic*., align=left]
\item be elected from amongst the committee members;
\item act in compliance with the Duties of the Chairperson (Bylaw 2.9.2);
\item and fulfill the duties in Bylaw 2.9.5.11.1;
\item A Deputy Chairperson (if applicable), who shall assume the duties of the Chairperson at the discretion of the Chairperson or the committee or in the absence of the Chairperson.
\end{enumerate}
\end{enumerate}
\item The Health Plan Committee will have:
\begin{enumerate}[label*=\arabic*., align=left]
\item A membership limit, as per Bylaw 2.9.4.2.2., set at 12 voting members, including the Chairperson and the Deputy Chairperson (if applicable).
\end{enumerate}
\item The Vice-President Student Services (Official Liaison, Ex-officio), President (Ex-officio), and SOGS Accounting Manager (Ex-officio), and Communications Administrator (Ex-officio) shall be non-voting members in accordance with Bylaws 1.6.4.2, 2.9.3.7., and 2.9.3.8.
\item All voting members of the Health Plan Committee shall be full and associate members of the Society nominated to the committee by the Society’s Council.    
\end{enumerate}

\subsection{Article II: Committee Management}
\begin{enumerate} [label*=\arabic*., align=left]	
\item The HPC will act in accordance with Bylaw 2.9.3.5 and 2.9.3.7 to determine quorum, Bylaw 2.9.3.9 to manage and maintain attendance, and Bylaw 2.9.4.2.1 to count votes.
\item Voting Policies
\begin{enumerate} [label*=\arabic*., align=left]	
\item Aside from the scheduled meetings, online voting is also permitted on the condition that it is for correcting spelling, grammar or wording mistakes on motions. Voting members shall be given one (1) business day to respond to an online vote, at which point the vote shall be considered concluded. If any voting member objects to business being voted on online, the voting shall be prohibited for that particular piece of business.
\item Committee members (including the Official Liaison, Chair(s), Deputy Chairperson (if applicable), and ex-officio members) can hold up to three (3) proxies.
\end{enumerate}
\item The committee shall:
\begin{enumerate} [label*=\arabic*., align=left]
\item The President shall:
\begin{enumerate} [label*=\arabic*., align=left]
\item be a non-voting member, ex-officio, of the HPC;
\item be a signing authority on the Health Plan Contract with the Vice-President Student Services.
\end{enumerate}
\item The Vice-President Student Services shall: 
\begin{enumerate} [label*=\arabic*., align=left]
\item be a non-voting member, Official Liaison and Ex-officio, of the HPC;
\item be a signing authority on the Health Plan Contract with the President.
\item be bound by Bylaws 2.1.10 and 2.1.2.4;
\item oversee the administration of the Health Plan in consultation with the President, the HPC, and the Plan Broker;
\item be the primary contact person for Plan Bidders in a tendering year;
\item work with the Accounting Manager, Administrative Assistant, and Communications Administrator to maintain website Health Plan information.
\end{enumerate}
\item The Chairperson shall:
\begin{enumerate} [label*=\arabic*., align=left]	
\item act in accordance with Bylaws 2.9.2 for general duties of a SOGS Committee Chairperson;
\item act in accordance with Bylaw 2.9.5.13 (“Health Plan Committee”);
\item call monthly meetings (unless otherwise agreed upon by the HPC);
\item assign the Deputy Chairperson (if applicable) or another Committee member to take meeting minutes in accordance with Society bylaws, “Minutes Writing Policy”;
\item distribute Committee minutes via the HPC listserv as per Bylaw 2.9.2.8.1;
\item submit HPC updates, AGM Reports, Final Reports, Surveys, and Health Plan Bid Shortlists, as approved by the HPC, for consideration at SOGS Council as per Bylaws 2.15.3.7 and 2.15.3.7.1;
\item liaise with the Vice-President Student Services, President, and Broker for any and all work related to the Health Plan (contracts, surveys, town halls, etc.);
\item update the HPC Chair Transitional Manual at the end of their term and submit it for review to the Vice-President Student Services before stepping down and/or graduating.
\end{enumerate}
\item Committee members shall:
\begin{enumerate}[label*=\arabic*., align=left]
\item act in accordance with Bylaw 2.9.3.9;
\item regularly attend committee meetings to the best of their ability;
\item participate in the committee’s projects to the best of their ability;
\item vote to approve minutes and motions, and in elections (e.g. HPC Chairperson).
\end{enumerate}
\item Maintaining Membership
\begin{enumerate}[label*=\arabic*., align=left]
\item The Communications Administrator shall oversee the HPC listserv and committee member list.
\item The Vice-President Student Services shall ratify committee members at Council and inform the HPC Chair about new members.
\item The Chairperson shall enforce SOGS Committee policies as per Bylaws 2.9.3. and 2.9.4. and inform the Vice-President Student Services when new members are added, and when members resign.
\begin{enumerate}[label*=\arabic*., align=left]
\item If the Chairperson position becomes vacant the Deputy Chairperson (if applicable) will serve as chair pro tempore until the next HPC meeting where an election to replace the Chair will take place.
\item If the Chairperson is temporarily unable to complete the roles and responsibilities of the chair position, the Deputy Chairperson (if applicable) will fulfill the roles and responsibilities of the Chairperson until the Chairperson returns.
\item The only circumstances in which the HPC may be temporarily chaired by the Official Liaison is for the purpose of conducting an election to select an existing member of the HPC to the position of Chair even if for a temporary, non-permanent and short-term basis, or until the Chair position is filled. 
\end{enumerate}
\item Committee Members shall:
\begin{enumerate}[label*=\arabic*., align=left]
\item act in accordance with Bylaw 2.9.3.9;
\item inform the Chairperson, Vice-President Student Services and copy the Communications Administrator if they wish to resign from the committee.
\end{enumerate}
\item Committee Archiving
\begin{enumerate}[label*=\arabic*., align=left]
\item The Communications Administrator will submit HPC minutes to the SOGS Public Dropbox.
\item The Vice-President Student Services will store HPC minutes and relevant documents in the SOGS Vice-President Student Services Google Drive folder under “Health Plan Committee”.
\end{enumerate}
\item Non-committee members may attend as non-voting guests if invited by the Chairperson. Committee members may also request that non-committee members attend as non-voting guests.
\item Bylaw 1.6.5. the Chairperson, and voting members may serve no more than 12 consecutive months without being ratified for a new council year.
\item Respectful Abandonment: In the event of the failure of a voting member of the committee to attend two meetings during their term either in person or by proxy, the Chairperson may remove the member from the committee in accordance with the protocols listed in Bylaw 2.9.3.9.
\end{enumerate}
\end{enumerate}
\end{enumerate}

\subsection{Article III: Operations}
\begin{enumerate}[label*=\arabic*., align=left]
\item Health Plan Opt-Ins / Opt-Outs
\begin{enumerate}[label*=\arabic*., align=left]
\item Opt-In/Opt-Out Deadlines: Health Plan opt-ins/opt-outs shall be permitted until the last day of class of the first semester in which a graduate student becomes enrolled at Western University.
\item Opt-In/Opt-Out Appeals: Health Plan opt-ins/opt-outs shall be permitted after the deadline under the following circumstances/conditions:
\begin{enumerate}[label*=\arabic*., align=left]
\item Proof of completion of non-full-time student status, such as completion of studies.
\item Proof of alternate health plan coverage (not including UHIP, OHIP, or provincial equivalent).
\item Under the discretion of the HPC.
\end{enumerate}
\end{enumerate} 
\item Health and Dental Plan (N.B. Fiscal year begins September 1)
\begin{enumerate} [label*=\arabic*., align=left]	
\item The HPC Official Liaison and the President are responsible for ensuring these policies are enforced.
\item General Procurement Policy
\begin{enumerate}[label*=\arabic*., align=left]	
\item The HPC shall act in accordance with Society bylaws on "Procurement."
\item The HPC shall specifically act in accordance with Society bylaws on "Request for Proposal."
\item The HPC shall sign a non-disclosure agreement for the duration of the process until the contract is executed and signed.
\end{enumerate}
\item Health Plan Procurement Policy
\begin{enumerate} [label*=\arabic*., align=left]	
\item The HPC shall act in accordance with Society bylaws on the "Health Plan."
\item The HPC shall act in accordance with Society bylaws on "Conflict of Interest."
\item In a non-tendering year, the HPC will devote its time to research and data collection in order to continue to improve the Health and Dental Plan.
\end{enumerate}
\item Health \& Dental Plan Timeline

\begin{tabular}{|l|l|l|}
\hline 
\multicolumn{3}{|l|}{\textbf{Milestone}} \\ 
\hline 
Prepare to Tender & October and November & See archived data \\ 
\hline 
Circulate RFP & First week in December & See Procurement Policy \\ 
\hline 
Receive Bidder Questions & Second week in January & See archived documents \\ 
\hline 
Respond to Questions & Third week in January & See archived documents \\ 
\hline 
Proposal/Bid Deadline & Second week of February & See Procurement Policy \\ 
\hline 
Evaluate Proposals/Bids & Third week of February & See archived documents \\ 
\hline 
Bidder Interviews & Fourth week of February & See archived documents \\ 
\hline 
Submit Shortlist to Council & Last Thursday of  March (Council) & See Bylaw 3.5.17.2 \\ 
\hline 
Final Report to Council & Last Thursday of \newline May (Council) & See archived documents \\ 
\hline 
\end{tabular}


\item Health \& Dental Plan Award Process

\begin{enumerate}[label*=\arabic*., align=left]	
\item Involves vetting of submitted bids in addition to a 45-minute interview of each bidder.
\item The HPC will construct its shortlist based on the following criteria:
\begin{enumerate}
\item Price -- 30\% (e.g. Lowest premium)
\item Specific Compliance -- 25\% (e.g. financial responsible model(s) for SOGS)
\item Quality -- 20\% (overall financial and service value to graduate students; coverage)
\item Terms and Conditions -- 10\% (e.g. blackout period, dispensing fee, family opt-ins
fees)
\item Experience -- 10\% (e.g. working directly with other Graduate Societies)
\item Other -- 5\% (Discounts, Network, Bursaries, Sponsorship, Promotional,
Communication, Administrative, Data Analytics, Flex Plans, Mental health/Wellness initiatives, etc.).
\end{enumerate}
\end{enumerate}
\item Graduate Student Mental Health and Wellness
\begin{enumerate}[label*=\arabic*., align=left]
\item Work in partnership with the Vice-President Student Services, Graduate Peer Support (GPS), and the Health
\& Dental Plan Broker in preparation for Graduate Wellness Week (October) and its initiatives.
\item During non-tendering years, the HPC will work in partnership with other SOGS committees to advocate on
behalf of graduate students in terms of their mental health and wellness.
\end{enumerate}
\end{enumerate}
\end{enumerate}