\section{Policy Committtee}

\subsection{Ratified}
November 11, 2020

\subsection{Mandate}
A Standing Committee of the Society (Bylaw 2.9.5.11), the Policy Committee is mandated with maintaining the Policy Manual, consulting on policy for standing and ad-hoc committees and commissions as well as other SOGS policies, and drafting motion-based policies. The Policy Committee works in conjunction with the Bylaws and Constitution Committee to ensure consistency and cohesion within the Society's unified governing documents.

\subsection{Membership}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item The Policy Committee shall have:
	\begin{longenum}[label*=\arabic*., align=left]	
	\item An Official Liaison, who shall be the President, in compliance with Bylaws 2.9.3.2 and
2.9.3.3.
	\item The Policy Committee will elect:
		\begin{longenum}[label*=\arabic*., align=left]	
		\item A Chairperson, who shall:
			\begin{longenum}[label*=\arabic*., align=left]	
			\item be elected from amongst the committee members;
			\item act in compliance with the Duties of the Chairperson (Bylaw 2.9.2), and;
			\item fulfill the duties in Bylaw 2.9.5.11.1.
			\end{longenum}
		\item A Deputy Chairperson (if applicable), who shall assume the duties of the Chairperson at the discretion of the Chairperson or the committee or in the absence of the Chairperson.
		\end{longenum}
	\item As per bylaw 2.9.4.2.2., the membership limit for the Policy Committee is set at 13 voting members, including the Chairperson and/or Deputy Chairperson.
	\end{longenum}
\item The Deputy Speaker shall be a voting ex-officio member (Bylaw 2.9.5.11.2).
\item The Ombudsperson shall be a non-voting ex-officio member (Bylaw 2.2.7.5).
\end{longenum}

\subsection{Article II: Committee Management}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 	
\item The Policy Committee will act in accordance with bylaw 2.9.3.5 and 2.9.3.7 to determine quorum, bylaw 2.9.3.9 to manage and maintain attendance, and bylaw 2.9.4.2.1 to count votes.
\item Voting Policies
	\begin{longenum}[label*=\arabic*., align=left]	
	\item Aside from the scheduled meetings, online voting is also permitted on the condition that it is for correcting spelling, grammar, or wording mistakes on motions. Voting members shall be given one (1) business day to respond to an online vote, at which point the vote shall be considered concluded. If any voting member objects to business being voted on online, the voting shall be prohibited for that particular piece of business.
	\item Committee members (including the Official Liaison, Chairperson, and ex-officio members) can hold up to three (3) proxies.
	\end{longenum}
\item Non-committee members may attend as non-voting guests if invited by the Chairperson. Committee members may also request that non-committee members attend as non-voting guests.
\item Respectful abandonment: In the event of the failure of a voting member of the committee to attend two meetings during their term either in person or by proxy, the Chairperson may remove the member from the committee in accordance with the protocols listed in bylaw 2.9.3.9.
\item Roles and Responsibilities
	\begin{longenum}[label*=\arabic*., align=left]	
	\item The Chairperson shall:
		\begin{longenum}[label*=\arabic*., align=left]	
		\item submit committee member names to Council each May for re-ratification (article 1.6.5.1.);
		\item sit, ex-officio, on the Bylaws and Constitution Committee.
		\end{longenum}
	\end{longenum}
\end{longenum}

\subsection{Article III: Operations}
\begin{longenum}[ label*=\thesubsection.\arabic*., align=left] 
\item The Policy Committee shall:
	\begin{longenum}[label*=\arabic*., align=left]
	\item review the motions database in order to discern and/or devise policy from it for systematic inclusion in a distinct Policy Manual which will be publicly available in the same manner as other documents of the Society;
	\item draft motion-based policies so that the original intents of motions are not substantially altered;
	\item react to motions of Council that affect the Policy Manual;
	\item advise committees on their policy manuals (bylaw 2.9.4.1.);
	\item advise and review other Society policy documents (e.g., Personnel Policy, Financial Policy, Grad Club Policy);	
	\item meet at least once between meetings of Council.
	\end{longenum}
\item The Chairperson (or designate) shall attend Council in order to discern and/or devise policy from passed motions for inclusion in the Policy Manual(s) related to them.
\end{longenum}














