\section{Sustainability Committee}

\subsection{Ratified}
April 25, 2019

\subsection{Mandate}
As per Bylaw 2.9.4.1., the Sustainability Committee is a standing committee of the Society of Graduate Students (SOGS). The Sustainability Committee shall strive to promote sustainability on and off Western campus by addressing ecological and social challenges at hand.

\subsection{Article 1: Membership}
\begin{enumerate}[label*=\arabic*., align=left]	
\item The Sustainability Committee shall consist of:
\begin{enumerate}[label*=\arabic*., align=left]	
\item One Chair or two Co-Chairs who shall act in compliance with the Duties of the Chairs as outlined in the Society’s Bylaws 2.9.2.
\begin{enumerate}[label*=\arabic*., align=left]
\item The Chair/Co-Chair positions shall be reviewed and voted upon each April by the committee, with a transition in May.
\item Chair/Co-Chair election process: Nominees shall submit a short statement of intent to committee members to vote on. Voting shall occur at a committee general meeting and shall be led by the Official Liaison.
\end{enumerate}
\end{enumerate}
\item An Official Liaison, who shall be the Vice President Advocacy, will oversee the operations of the Sustainability Committee in compliance with the Society’s Bylaw 2.9.3.2.
\item The committee shall consist of a maximum of 12 voting members, including the Chair/Co-Chairs.
\item Committee members will each be elected one position per year (based on the current needs of the committee). Positions shall include:
\begin{enumerate}[label*=\arabic*., align=left]
\item Promotions, Advertisement and Social Media Manager(s), who shall be responsible for creating and distributing promotional material.
\item A Recording Secretary, who shall be responsible for keeping committee meeting minutes.
\item Event Coordinator(s), who shall be responsible for event logistics.
\item Communication Officer(s), who shall be responsible for maintaining contact with collaborators.
\end{enumerate}
\item All committee members shall:
\begin{enumerate}[label*=\arabic*., align=left]
\item Attend regular meetings.
\item Actively participate in meeting discussions.
\item Assist in the planning and execution of all committee initiatives (2-4 per year).
\item Reply to e-mail requests sent by the Chair(s) or Vice President Advocacy.
\end{enumerate}
\item Meetings are comprised of members of the Sustainability Committee including the Chair/Co-Chairs and the Vice President Advocacy. Non-committee members may attend as non-voting guests with consent of the Chair(s).
\item Committee voting can be conducted by email or mail if a member is unable to vote in person (as per Bylaw 2.9.4.2.1.).
\item Respectful Abandonment: In the case that a member of the committee does not attend two meetings without explanation or proxy. As per Bylaw 2.9.2.9., the Chair(s) will keep a record of committee meetings and member attendance.
\item The Chair(s) may, at the discretion of the other committee members, remove a member from the committee if that person does not comply with committee responsibilities as outlined in 1.5.2.-1.5.4., and/or does not reply to a follow-up e-mail sent by the Chair(s) within two weeks.
\end{enumerate}

\subsection{Article 2: Committee Responsibilities}
\begin{enumerate}[label*=\arabic*., align=left]	
\item The Sustainability Committee shall:
\begin{enumerate}[label*=\arabic*., align=left]	
\item Educate the Society’s members about sustainability.
\item Conduct an ongoing sustainability assessment of SOGS, including The Grad Club, SOGS Office, and the graduate community to determine areas of improvement.
\item Identify efforts to address concerns identified through the sustainability assessment.
\item Plan and executive 2-4 sustainability initiative(s) each year.
\item Collaborate where appropriate with other student sustainability groups on campus to promote sustainability at Western.
\item Collaborate where appropriate with Facilities Management, Sustainability Western, and other relevant stakeholders on sustainability initiatives at Western.
\end{enumerate}
\end{enumerate}
